\chapter{Introduction}

Historically, the accountability of software engineers has not been an issue of
concern for three reasons. First, software was originally used only by experts
and corporations for limited and purposed uses beyond the reaches of end
users and the general public \cite{Leveson95}. Second, processor instruction 
sets were primitive and software programs were very simple \cite{Storey95}. 
Finally, the availability of attorneys with applicable expertise to handle 
software cases has been rare \cite{Armour93}. Today's society no longer observes
these limitations.

Organizations today are in the business of building better products faster,
cheaper, and more efficiently. As a result of society's demands, these
organizations find themselves increasingly relying on software for the benefits
of rapid deployment and efficiency over traditionally engineered physical
components. Over the years, software has almost become an ideal product.
Software can be created quickly and easily. There are little to no material
costs associated with producing software and there is no deterioration over
time. It can be replicated cheaply once written and, since the inception of the
Internet, it is more mutable (e.g. updateable) than ever. By now, computers
have progressed to the point where using software in solutions not only
possible, but more economically feasible than using solely hardware components 
\cite{Baase97}. Software is oftentimes the only feasible alternative for solving
certain problems.

Complexity of software programs has also increased. Significant work in
programming only began in the 1950s, and mainstream software use didn't begin
until recently. But over time, knowledge of software has grown exponentially
and with developments like higher-level programming languages, object-oriented
design, and open source libraries, the complexity of software has equally
increased.

Thirdly, the number of computer-savvy attorneys is growing. In 1974, the
American Bar Association formed a section of Science \& Technology Law to provide
a forum for addressing issues at the intersection of law, science, and
technology. The section now has over 10,000 members. 10 of the 23 committees
within the section are devoted to E-Commerce and IT Law, focussing on issues
including computer law and cyber crime \cite{SCITECH}. Representation of
computer science and other related undergraduate majors in law schools is also
growing\footnote{Dr. Clark Turner, a computer science professor at the
California Polytechnic State University (Cal Poly) has seen at least one
computer science graduate apply to law school during his recent years of
teaching.}.

With these factors mitigated, society will encounter legal disputes involving
software. Our culture continues to use software in risky situations and we are
getting ahead of our readiness to handle the repercussions. Microprocessors
and software are being used to control prosthetic limbs \cite{Graupe78}, to help
restore sight sight to the blind \cite{Fox95}, to automate the braking systems
in cars \cite{Hurtig94}, and even to treat cancer patients with radiation
\cite{Leveson93}. Because of the rising use of software in industry, its
increased complexity in implementation, and growth of qualified professionals,
the risk of accidents resulting in a legal complaint will appear. But society
has not yet dealt with the full implications of liability for software related
accidents.

We focus our research on software testing. Are the processes that we use to test
software legally sufficient in fulfilling our responsibilities as professionals?
How does one \textit{decide} whether or not they are? After laying a foundation
of knowledge in Chapter \ref{C:Background}, we can tightly define this 
``\textit{deciding}'' problem in Chapter \ref{C:Motivation} and propose a solution
in Chapter \ref{C:Software}.

