\section{Products Liability}\label{S:Liability}
The term \textit{products liability} broadly applies to the liability of a
manufacturer or seller for injury to a buyer caused by a product that has been
sold \cite{Testing2005}. A \textit{product} usually refers to physical 
merchandise that can be purchased\footnoteremember{putnam}{\textit{Winter v. 
G.P. Putnam's Sons}, 938 F.2d 1033.\\In this case, Wilhelm Winter became
critically ill from eating mushrooms that he picked relying on the information
in a book published by Putnam. The judge favored in the side of Putnam, claiming
that the contents of \textit{The Encyclopedia of Mushrooms} is not a product 
that can be liable because the law does not take into consideration the unique
characteristics of ideas and expression. However, the plaintiff's argument was
strong when the book was analogized to aeronautical charts - graphical
depictions of technical and mechanical data. They are intended to be used while
engaging in hazardous activity. The discussion also mentions that
\textit{software} may be considered a product for this same reason. Software
that ``\textit{fails to yield the result for which it was designed}'' may be
considered under products liability}. Officially, a product is defined as 
\begin{quote}
``\textit{\ldots tangible personal property distributed commercially for use or
consumption and other items, such as real property and electricity, when the
context of their distribution and use is sufficiently analogous to the
distribution and use of tangible personal property\ldots}\footnote{Restatement
Third, Torts: Products Liability \S 19(a).}''
\end{quote}

In the case of safety-critical systems, software is usually embedded in
some machine or hardware device \cite{Leveson95} that is sold as a 
product\footnote{59 A.L.R.5th 461.}. When viewed from this standpoint, software
is less analogous to pure thoughts and expressions and may be considered a
product for products liability cases\footnoterecall{putnam}. Many forms of
products liability exist, including \textit{contract}, \textit{strict}, and
\textit{negligence}.

\textit{Contracts}, often in the form of software warranties or End User License
Agreements (EULAs), are issued to assure customers that the products purchased
will perform as stated \cite{Armour93}. Contract law can be dismissed because,
as described in the next section, negligence liability applies regardless of
what terms are steted in any contract. Even if a contract disclaims end-user
risk, manufacturers are still held accountable and cannot absolve themselves
from liability from defects \cite{Ryan03}.

\textit{Strict Liability} applies to any product that is defective, regardless
of the amount of care used in the process to manufacture it\footnote{63 Am. Jur.
2d Products Liability \S 90.}. While strict liability is interesting
\cite{Turner00}, this research is concerned with the \textit{processes} and
\textit{tradeoff} analysis involved with developing and testing software. Since
these aspects of software engineering are behavioral, they fall under the
jurisdiction of negligence law.

\subsection{Negligence}\label{SS:Negligence}
While the development of products liability based on breach of warranty and
strict products liability doctrines have, to an extent, reduced the utility of
negligence because in these forms the proof of specific negligence is
unnecessary\footnote{Am. Law. Prod. Liab. 3d, Chapter 10, \S 10:1.}, we apply
negligence law to our research. Negligence is concerned with process, not with
product. The question is not whether software development can be applied to
negligence law, but if negligence law can apply to software development. The
legal term \textit{negligence} refers to, in general, careless conduct. 
Scholars describe negligence more specifically as\footnote{57A Am. Jur. 2d
Negligence \S 5.}:\singlespace
\begin{itemize}
 \item the existence and violation of a legal duty to use care, proximately 
 causing injury to another.
 \item the failure to exercise the degree of care demanded by the circumstances.
 \item the breach of a duty to another to protect him or her from the particular
 harm that ensued.
 \item the want of that care the law prescribes under the particular
 circumstances existing at the time of the act or omission which is involved.
\end{itemize}\doublespace

Negligence can be applied to many different scenarios beyond products
liability. An intoxicated driver who disobeys traffic laws may be negligent
towards other citizens of the road\footnote{\textit{People v. Townsend}, 214
Mich. 267, 272, 183 N.W. 177.}. A teacher who fails to demonstrate safety
precautions to his students in wood shop may be liable for
negligence\footnote{\textit{Voorhies v. Conroe Independent School Dist.}, 610
F.Supp. 868.}. An engineer who does not adequately inspect his high-integrity
product can be negligent to his clients\footnote{\textit{Ford Motor Co. v.
Mondragon}, 271 F.2d 342.}. This research focuses on the negligence constrains
as they apply to products liability.

Negligence is easiest to determine when some standard of care stated by the
profession is available. Since no such standard exists for software engineering,
a more qualitative approach must be taken. Figure \ref{fig:handtest} shows a
formula that equates negligence in terms of unreasonable behavior.  According to
the Learned Hand test\footnote{\textit{United States v. Carroll Towing Co.}, 159
F.2d 169.\\ Judge Learned Hand created this guideline to determine the amount of
duty owed in a negligence dispute. In the case, the United States sought
compensation for flour that was lost when a barge carrying the cargo sunk. The
barge company was partly responsible because no workers were present on the
barge when it sank, which may have prevented the barge from sinking.
Qualitatively, the amount it would have cost to keep a worker on the barge would
have been less than the product of the probability that the barge sank and the
amount of damages incurred from it sinking.}, an organization that develops
safety-critical software has a duty to spend at least the amount of time and
resources equivalent to the product of the severity of harm and the likelihood 
that it will happen. If they do not, then their actions are negligent. The
Learned Hand test is an important metric because it provides a way to evaluate
the existence of negligence without the presence of a strict standard.

\begin{figure}
\begin{narrow}{-1.5in}{-1.5in}\begin{center}
\begin{tabular}{|l|}
\hline
	Let \textbf{B} be the burden (expense) of preventing a potential accident.\\
	Let \textbf{L} be the severity of the loss if the accident occurs.\\
	Let \textbf{P} be the probability of the accident.\\[6pt]
	Then \textit{failure to attempt to prevent a potential accident is 
	unreasonable if}\\[8pt]

      \centerline{\(B < P \times L\)}
\\[3pt]
\hline
\end{tabular}
\end{center}\end{narrow}
\caption{The Learned Hand Test for Negligence}
\label{fig:handtest}
\end{figure}

\subsubsection{Elements of Negligence}\label{SS:Elements}
The applicability of negligence requires that certain conditions exist and the
laws of negligence can only be invoked in these situations. The prerequisites,
or prima facie elements, of a negligence case are \cite{Dobbs01}:

\singlespace
\begin{enumerate}
 \item there exists a duty of care (or duty to protect)
 \item the defendant breaches this duty with unreasonably risky conduct
 \item the defendant's conduct resulted in harm to the plaintiff
 \item the negligent conduct was a proximate cause of harm
 \item legally recognized damages or injury exist
\end{enumerate}
\doublespace

First, a negligence case calls for an actual duty of care owed to a plaintiff.
There may be a question about how much care is owed in a given situation, but
there are circumstances in which there is no duty owed that bears on the harm a
plaintiff suffers. Judges decide whether or not this duty exists.

Also, there must be a breach of this duty of care owed. A defendant who behaves
reasonably and exercises the necessary care required by law will not be
negligent even if the plaintiff is harmed.

The defendant's negligence must be the cause of the harm suffered by the
plaintiff. An careless engineer who does not test his product is not negligent
to the user who is injured by tripping over the machine. In addition, the cause
must not only be cause in fact, but a proximate, or primary, cause of the harm
suffered.

Finally, actual damages or injuries must be suffered for a negligence case to
follow suit. This can include personal injury or damages to property.

\subsubsection{Software Fulfills the Prima Facie}

It is not a stretch to conclude that defective software in a safety-critical
situation will be subject to negligence allegations. The developing
organization clearly owes a duty of care to its customers. Since the software
will be used to perform tasks that can potentially cause harm, its users expect
a reasonably prudent amount of care from its developers.

The remaining elements are assumptions that this research seeks to evaluate.
Performing tests is a large part of quality assurance for software and doing it
correctly can mitigate the risk of unreasonably breaching a duty of care.

\subsubsection{Professional Negligence and Software Licensing}
Talk about computer malpractice \cite{Kaner96}.
