\section{Results}\label{results}
We have examined the legal implications of developing software for
safety-critical systems and deduced constraints on software processes in
accordance to these implications. In order for an organization to develop 
software prudently for use in safety-critical environments, they must engage in
certain activities. We describe one such activity: the commenting practices of
software developers.

In addition, we have designed the requirements for a system that will help
organizations fulfill some of the legal constraints for software organizations
in the safety-critical realm. If a system that implements our design were in
place, an organization will be able to provide adequate documentation of design
decisions during the software development process. Our system allows for 
software developers to easily write versioned, multiple-code-associated comments
in real-time without severely disrupting the  development process or impeding
the readability of the code base.

\subsection{Drawbacks}

\subsubsection*{Documentation Attitude}
The success of this system requires a forward-thinking attitude of commitment to
documentation. Most domains of software engineering spend minimal time with
formal documentation methods in an effort to achieve faster turnaround and
short-term gain through quick (and often rushed) implementation cycles. This
disregard to the care of formal documentation may yield better immediate gains,
but ultimately degrades the quality of the implementation, reusability of the
software,  and traceability of design decisions.

\subsection{Future Work}
At the time of this paper's writing, the proposed system has yet to be
implemented. A proof-of-concept implementation should be built to confirm the
feasiblity of the system. In addition, it may be helpful to perform a formal
study, perhaps through industry survey, to guage the acceptance of the system in
real industry work.

That noted, the proposed system has a vast potential if adopted by the industry.
The key to this solution is the association database. Such a database can be
exploited to provide a richer feature set beyond the mere real-time commenting 
capabilities of the proposed system. The automated techniques in 
\cite{Antoniol1999, Antoniol2000} could introduce the use of associated comments
to provide richer, more accurate associations. Annotations like those used in
\cite{Javadoc} can be introduced into associated comments to provide more formal
documentation formats with richer semantic metadata.

\subsection{Conclusions}